HPC--101\\Onboarding

### 2018-04-23 hpc_101/sections/07_policies.tex
correction to purge policy

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 30 days.
\begin{itemize}
 \item What in \ctilde/lus/ is subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} Everything but directories and files between 1 byte and 32 Kilobytes are subject to the purge policy.
   \end{itemize}
%\item How frequently are files for purged?
%   \begin{itemize}
%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%   \end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}

>>>>

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.

\begin{itemize}
\item What in \ctilde/lus/ is subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} Everything but directories.
   \end{itemize}
\item When will my files be purged?
  \begin{itemize}  
    \item \textbf{Answer:} Files greater than or equal to 1 Megabytein size  or are empty (0 bytes) that are 35 days old
    \item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  \end{itemize}
\item What is the age based on?
   \begin{itemize}
   \item \textbf{Answer:} Age of file is based on creation time
   \end{itemize}

%\item How frequently are files for purged?
%   \begin{itemize}
%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%   \end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}
